---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file. -->
<!-- The code to render this README is stored in .github/workflows/render-readme.yaml -->
<!-- Variables marked with double curly braces will be transformed beforehand: -->
<!-- `packagename` is extracted from the DESCRIPTION file -->
<!-- `gh_repo` is extracted via a special environment variable in GitHub Actions -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = file.path(c("man", "figures", "README-")),
  out.width = "100%"
)
```

# _{{ packagename }}_ <img src="man/figures/logo.svg" align="right" width="120" />

<!-- badges: start -->
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/license/mit/)
[![R-CMD-check](https://github.com/{{ gh_repo }}/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/{{ gh_repo }}/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/{{ gh_repo }}/branch/main/graph/badge.svg)](https://app.codecov.io/gh/{{ gh_repo }}?branch=main)
[![lifecycle-{{ recon }}](https://www.reconverse.org/images/badge-{{ recon }}.svg)](https://www.reconverse.org/lifecycle.html#{{ recon }}) 
<!-- badges: end -->

_{{ packagename }}_ is an R package to convert numbers written as English, French or Spanish words from `"zero"` to `"nine hundred and ninety nine trillion, nine hundred and ninety nine billion, nine hundred and ninety nine million, nine hundred and ninety nine thousand, nine hundred and ninety nine"` from a character string to a numeric value.

<!-- This sentence is optional and can be removed -->
_{{ packagename }}_ is developed at the [{{ department }}]({{ department_url }}) at the {{ institution }} as part of the [Epiverse-TRACE program](https://data.org/initiatives/epiverse/).


## Installation

You can install the development version of _{{ packagename }}_ from
[GitHub](https://github.com/) with:

```{r eval=TRUE}
# install.packages("pak")
pak::pak("{{ gh_repo }}")
library("numberizeR")
```

## Example

These examples illustrate the current functionality.

```{r eval=TRUE}
# numberize the French string "zéro"
numberize("zéro",  lang = "fr")

# numberize the Spanish string "Siete mil quinientos cuarenta y cinco"
numberize("Siete mil quinientos cuarenta y cinco", lang = "es")

# numberize the English string "nine hundred and ninety-nine trillion, nine hundred and ninety-nine billion, nine hundred and ninety-nine million, nine hundred and ninety-nine thousand, nine hundred and ninety-nine" # nolint: line_length_linter.
formatC(numberize("nine hundred and ninety-nine trillion, nine hundred and ninety-nine billion, nine hundred and ninety-nine million, nine hundred and ninety-nine thousand, nine hundred and ninety-nine"), big.mark = ",", format = "fg") # nolint: line_length_linter.
```

## Development

### Lifecycle

This package is currently *{{ recon }}*, as defined by the [RECON software
lifecycle](https://www.reconverse.org/lifecycle.html).

  > [!NOTE] 
  >{{ recon_description }}

### Contributions

Contributions are welcome via [pull requests](https://github.com/{{ gh_repo }}/pulls).

### Code of Conduct

Please note that the _{{ packagename }}_ project is released with a 
[Contributor Code of Conduct](https://github.com/epiverse-trace/.github/blob/main/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.